---
title: "Lab of the 24th"
format: html
editor: visual
execute :
  keep-md: TRUE
  echo: FALSE
  warning: FALSE
---

```{r, results='hide'}
#Setup

here::i_am("r-101-grade-analysis.Rproj")
library(here)
library(readr)
library(ggplot2)
library(dplyr)
library(tidyr)
library(labelled)
library(kableExtra)
library(viridis)
library(RColorBrewer)
library(forcats)
```

<center>

# Dplyr-Lab (Lab of the 24th)

</center>

<center>GitHub link (URL) : <https://github.com/CBZ1310/r-101-grade-analysis></center>

## Exercise 1

### Question 1

```{r}
grades <- read_csv("grades.csv")

```

```{r,results='hide'}
Vn<- names(grades)
Vn
```

### Question 2

```{r}
rst <- grades %>% 
  summarize("Min" = min(Exam, na.rm = TRUE), 
            "Median" = median(Exam, na.rm = TRUE), 
            "Max" = max(Exam, na.rm = TRUE), 
            "Mean" = mean(Exam, na.rm = TRUE), 
            "Standard Deviation" = sd(Exam, na.rm = TRUE))

var_label(rst) <- "Exam's result mean statistics"

knitr::kable(rst, caption = "Exams - statistics", format="html", align = "c", digits = 2) %>%
  kable_minimal()


```

```{r}
cv_exam <- sd(grades$Exam, na.rm = TRUE)/mean(grades$Exam, na.rm = TRUE)*100
var_label(cv_exam)<- "Coefficient of variation of the exam's grades"

cat("Complementary data - Coefficient of variation =", cv_exam,"%")
```

### Question 3

```{r}
Dnc <- sum(is.na(grades$Exam))
                         
var_label(Dnc) <- "Do not come to the exam"

cat(Dnc, "students do not come at the exam")
```

### Question 4

```{r}
grades %>% filter(!is.na(Exam)) %>% ggplot(aes(x = Exam)) + 
  geom_bar(fill="pink")+ 
  geom_label(stat = "count", aes(label = ..count..), fill = "pink", color = "black", size = 2.5, vjust = -0.3, label.padding = unit(0.2, "lines")) + 
  labs(title = "Distribution of the Grades", x="Grades", y="Count")+
  theme(plot.title = element_text(hjust = 0.5))+
  theme_minimal()
```

```{r}
grades %>% filter(!is.na(Exam)) %>% ggplot(aes(x = Exam, y= "count")) +
  geom_boxplot(fill="pink") +
  labs(title = "Distribution of the Grades", x = "Grades", y = "Count") +
  theme_minimal()
```

### Question 5

```{r, results='hide'}
Vn
```

```{r}
Nst <- grades %>%
  group_by(Group) %>% 
  summarize(Total_count=n(), "Student who comes to the exam"=sum(!is.na(Exam)), "% of Student whp comes" = sum(!is.na(Exam))/n()*100) %>%
  arrange(desc(Total_count))

var_label(Nst) <- "Number of student by group"

knitr::kable(Nst, caption = "Number of students by group", format = "html", align = "c", digits = 2) %>%
  kable_minimal()
```

### Question 6

```{r}
grades%>% ggplot(aes(x=Group)) + 
  geom_bar(fill="white") + 
  labs(title ="Number of students by group", x="Group", y="count") + 
  geom_label(stat = "count", aes(label = ..count..), fill = "pink", color = "black", size = 2.5, vjust = -0.3, label.padding = unit(0.2, "lines")) +
  theme_dark()
```

```{r}
grades_2 <- grades %>%
  mutate(Come_to_the_exam = case_when(is.na(Exam) ~ "FALSE", Exam == "" ~ "",TRUE ~ "TRUE"))

grades_2 %>% ggplot(aes(x=Group, fill=Come_to_the_exam)) + 
  geom_bar() + 
  geom_text( stat = "count",  aes(label = stat(count)),position = position_stack(vjust = 0.5),color = "white", size = 3) +
  labs(title ="Number of students by group detailed by participation to the exam", x="Group", y="count") + 
  scale_fill_manual(values = c("TRUE"="lightgreen", "FALSE"="darkgrey")) +
  theme_minimal()
```

### Question 7

```{r}
grades%>%
  filter(!is.na(Exam)) %>%
  ggplot(aes(x=as.character(Group),y=Exam, fill=Group)) + 
  geom_boxplot()+
  geom_hline(yintercept = 10, color = "green", size=1, linetype="dashed")+ 
  labs(title ="Grade by group",subtitle = "(the green line emphasizes the moment when a grade = 10)", x="Group", y="Grades")+
  theme_dark()+ 
  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 1))

#I add as.character because I want it my x axis to be in a approximatively alphabetical order to be able to find a group more easely
```

```{r, fig.width=12, fig.height=24}
grades%>% filter(!is.na(Exam))%>% 
  ggplot(aes(y = Exam, fill = Group)) +
  geom_bar()+
  geom_hline(yintercept = 10, color = "green", linetype="dashed", size=1) +
   labs(title ="Grade by group",subtitle = "(the green line emphasizes the moment when a grade = 10)", x="Group", y="Grades")+ 
  facet_wrap(~as.character(Group), ncol=4)+
  theme_minimal()
```

Grade is a discrete value so the following result is more than imperfect but I find easely to read the previous facet with geom_density

```{r, fig.width=12, fig.height=24}
grades%>% filter(!is.na(Exam))%>% 
  ggplot(aes(y = Exam, fill = Group)) +
  geom_density(alpha=0.4) +
  geom_hline(yintercept = 10, color = "green", size=1)+
 labs(title ="Grade by group",subtitle = "(the green line emphasizes the moment when a grade = 10)", x="Group", y="Grades") + 
  facet_wrap(~as.character(Group), ncol=4)+
  theme_minimal()
```

### Question 8

```{r}

G_Dnc <- grades %>%
  group_by(Group) %>%
  summarize(`Missed Exam` = sum(is.na(Exam))) %>%
  arrange(desc(`Missed Exam`))

                         
var_label(G_Dnc) <- "Do not come to the exam by Group "

knitr::kable(G_Dnc, caption = "Number of students having missing exam by group", format = "markdown")
```

### Question 9

```{r}
G_Dnc %>% 
  ggplot(aes(x = as.character(Group), y = `Missed Exam`)) + 
  geom_col(fill="darkcyan") + 
  geom_text(aes(label = `Missed Exam`), vjust = -0.5, color = "black") + 
  labs(title = "Number of students who does not participate at the Exam by group", x = "Group", y = "Count") +
  theme_minimal()

```

### Question 10

```{r, output=FALSE}
grades_long_format <- grades %>%
  pivot_longer(cols = -c(Id,Group), names_to="Studied_Variable", values_to = "value")
  
```

### Question 11


The number of missing grades, when all value = NA is are taking into account, is `r {sum(is.na(grades_long_format$value))}`. Moreover, `r {sum(is.na(filter(grades_long_format, Studied_Variable == "Exam" )$value))}` student does not have grade for the "Exam" vairable.

### Question 12
```{r}
Na_glf <- grades_long_format %>% 
  group_by(Id) %>%
    summarise(Missing_grades = sum(is.na(value))) %>% 
    arrange(desc(Missing_grades))

var_label(Na_glf)<- "Missing Grades by student (long format)"

Na_glf %>%
  ggplot(aes(x=Id,y=Missing_grades))+
  geom_col(fill="darkgrey")+
  labs(title="Number of missing grades by student", x="Student's ID", y="Missing grades")+
  theme_minimal()

```

### Question 13
```{r}
Na_glf_group <- grades_long_format %>% 
  filter(Studied_Variable=="Exam")%>%
  group_by(Group) %>%
  summarize(Missed_Exam=sum(is.na(value))) %>%
  arrange(desc(Missed_Exam))

var_label(Na_glf_group) <- "Missing grades by grup"

knitr::kable(Na_glf_group, caption = "Missing grades by group", format = "html") %>%
  kable_minimal()
```


### Question 14


### Question 15

### Question 16

### Question 17

### Question 18


